---
title: 'Lesson 1 - Part 3: Basic operation'
author: "ZYY"
date: "2021年6月4日"
output: html_document
---
#Interfaces to the Outside World

* **file**, opens a connection to a file.
* **gzfile**, opens a connection to a **file compressed with gzip**
* **url**, opens a connection to a webpage

**file** has a few arguments:
```{r}
str(file)
```
* **description** is the name of the file.
* **open** is a code indicating:
  + **“r”** read only
  + **“w”** writing (and initializing a new file)
  + **“a”** appending
  + **“rb”, “wb”, “ab”** reading, writing, or appending in binary mode (Windows)
  
e.g. con <- file("foo.txt", "r"), then **con** can be read the same as "foo.txt"

#Reading Data

## **read.table**, **read.csv**, for reading tabular data
The most common functions for reading data. Reading data in columns and rows format and return data frames in R.
* **file**, the name of a file, or a connection

* **header**, logical indicating if the file has a header line.

* **sep**, a string indicating how the columns are separated,like ",", or tab, or space.

* **colClasses*""**, a character vector indicating the class of each column in the dataset, like the first column is logical and the next is integer. It is  not necessary.

* **nrows**, the number of rows in the dataset. Not required.

* **comment.char**, a character string indicating the comment character.The default symbol is "#".

* **skip**, the number of lines to skip from the beginning.

* **stringsAsFactors**, should character variables be coded as factors? The default is TRUE. 

**read.csv** is identical to read.table except that **the default separator is a comma**.

###When facing larger datasets:
*  Make a rough calculation of the memory required to store your dataset. If the dataset is larger than the amount of RAM on your computer, you can probably stop right here.
*  Set **comment.char = ""** if there are no commented lines in your file
*  Use the **colClasses** argument. If all of the columns are **“numeric”**, for example, then you can just set **colClasses = "numeric"**.If not：

initial <- read.table("datatable.txt", nrows = 100) #Read the first 100 rows
classes <- sapply(initial, class)                   #use the class function to know the class of each column
tabAll <- read.table("datatable.txt",               #Re-read with the colClasses 
 colClasses = classes)

* **nrows**can helps with memory usage.A mild overestimate is okay.

>Calculating Memory Requirements Calculating Memory Requirements

I have a data frame with 1,500,000 rows and 120 columns, all of which are numeric data. Roughly, how much memory is required to store this data frame?

1,500,000 × 120 × 8 bytes/numeric

= 1440000000 bytes

= 1440000000/2^20^  bytes/MB

= 1,373.29 MB

= 1.34 GB

Twice as much memory of dataset is needed when using **read.table**.

##  **readLines**, for reading lines of a text file.
It gives you text in as a character vector in R. It can be useful for reading in lines of webpages.
```{r}
## This might take time
con <- url("http://www.jhsph.edu", "r")
x <- readLines(con)
head(x)
```

##  **source**, for reading in R code files (inverse of dump)

##  **dget**, for reading in R code files (inverse of dput)

##  **load**, for reading in saved workspaces

##  **unserialize**, for reading single R objects in binary form

#Writing Data
There are analogous functions for writing data to files
**write.table,writeLines,save,serialize**

##Textal Format: **dump** and **dput**
Unlike writing out a table or csv file, dump and dput preserve the **metadata** (sacrificing some readability), so that another user doesn’t have to specify it all over again.
### **dput** for output - **dget** to read it back.
```{r}
y <- data.frame(a = 1, b = "a")
dput(y)
dput(y, file = "y.R")
new.y <- dget("y.R")
new.y
```
### **dump** for output - **source** for input
**dump**-**source** can be used for multiple objects while **dput**-**dget** can only be used on a single object.
```{r}
x <- "foo"
y <- data.frame(a = 1, b = "a")
dump(c("x", "y"), file = "y1.R") 
rm(x, y)    #remove x and y
source("y1.R")
y
x
```

#Subsetting

* **[** always returns an object of **the same class as the original**; can be used to select **more than one**
element (there is one exception).
* **[[** is used to extract elements of a **list** or a **data frame**; it can only be used to extract a **single**
element and the class of the returned object will **not** necessarily be a list or data frame.
* **$** is used to extract elements of a list or data frame by **name**; semantics are similar to that of [[.
```{r}
x <- c("a", "b", "c", "c", "d", "a")
x[1]
x[1:4]
x[x > "a"]
u <- x > "a"
x[u]
```

##Subsetting Lists
```{r}
x <- list(foo = 1:4, bar = 0.6)
x[1]        #for **[**, the return is also a list.
x[[1]]      #When using **[[**, only the sequence is returned.
x$bar       #only extract the elements with the name "bar", so the output is a number.
x[["bar"]]  #The same as $.
x["bar"]    #The output is a list.
```

When extracting multiple elements, **"["** is the only choice.
```{r}
x <- list(foo = 1:4, bar = 0.6, baz = "hello")
x[c(1, 3)]
```

The **[[** operator can be used with **computed indices**; $ can only be used with **literal names**.
```{r}
 x <- list(foo = 1:4, bar = 0.6, baz = "hello")
 name <- "foo"
 x[[name]] ## computed index for ‘foo’
 x$name ## element ‘name’ doesn’t exist!
 x$foo
```

The **[[** can take an **integer sequence**.
```{r}
x <- list(a = list(10, 12, 14), b = c(3.14, 2.81))
x[[c(1, 3)]]
x[[1]][[3]]
x[[c(2, 1)]]
```

##Subsetting a Matrix
Matrices can be subsetted in the usual way with (i,j) type indices.Indices can also be missing.
```{r}
x <- matrix(1:6, 2, 3)
x[1, 2]
x[1, ]
```
By default, when a single element of a matrix is retrieved, it is returned as **a vector of length 1** rather
than a 1 × 1 matrix. This behavior can be turned off by setting **drop = FALSE**. Similarly, subsetting a single column or a single row will give you a vector, not a matrix (by default).
```{R}
x <- matrix(1:6, 2, 3)
x[1, 2]
x[1, 2, drop = FALSE]
x[1, ]
x[1, , drop = FALSE]
```

##Subsetting with Partial Matching 
Partial matching of names is allowed with **[[** and **$**.
```{r}
x <- list(aardvark = 1:5)
x$a          #searching for the name with "a"
x[["a"]]     #searching for the name "a"
x[["a", exact = FALSE]] #seaching for the closest name  to "a" 
```

##Removing NA values
Common case:
```{r}
x <- c(1, 2, NA, 4, NA, 5)
bad <- is.na(x)
x[!bad]
```
When nultiple objects
```{r}
x <- c(1, 2, NA, 4, NA, 5)
y <- c("a", "b", NA, "d", NA, "f")
good <- complete.cases(x, y)  #whether in both objects, the value is not missing
good
x[good]
y[good]
```

#Vectorized Operation
Many operations in R are **vectorized** making code more **efficient, concise, and easier to read**.
```{r}
x <- 1:4
y <- 6:9
x + y
x > 2
x >= 2
y == 8
x * y
x / y
```

For **matrices**
```{r}
x <- matrix(1:4, 2, 2)
y <- matrix(rep(10, 4), 2, 2)
x * y ## element-wise multiplication
x / y
x %*% y ## true matrix multiplication
```


