---
title: "Overview of R"
author: "ZYY"
date: "2021年6月2日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background
When you want to get the **working directory**:
```{r }
getwd()
```
The reading and writing file should/will be in your working directory. If not, you will get a error message saying no such file or directory.

You can change your working directory in R in **File menu - Change dir**, then you can use dir command to list the files in working directory
```{r}
dir()
```

Besides files, you should also make sure that your r code or function in the working directory so that you can use it in the console window.
You can copy these codes into console window and run them or you can save them as an **.R** file, and use **source("filename.R")** command to run.

##Getting Started and R Nuts and Bolts

>Learning Objectives

By the end of week 1 you should be able to:

*  Install the R and RStudio software packages
*  Download and install the swirl package for R
*  Describe the history of the S and R programming lectures
*  Describe the differences between atomic data types
*  Execute basic arithmetic operations
*  Subset R objects using the "[", "[[", and "$" operators and logical vectors
*  Describe the explicit coercion feature of R
*  Remove missing (NA) values from a vector

###Overview and History if R
what is **R**?
It's basically R is a dialect of **S**.

>Then what is **S**?

* Developed by John Chambers in 1976
* An internal statistical analysis environment.
* A FORTRAN library for statistical routines.
* Rewrited in the C language, i.e. Version 3,in 1988 with all the **statistical analysis functionality**.John Chambers and Trevor Hastie also published a semial book in the same year, called *the Statistical Models in S*, referred to **the white book** as well.
* *The book Programming with Data*(the green book) and Version 4 of S is released by John Chambers in 1998.

R is an implementation of the S language, in 1993 Bell Labs.

####R
>History of R

* 1991: Created in New Zealand by **Ross Ihaka** and **Robert Gentleman**.
* 1993: First announcement of R to the public
* 1995: Free software
* 2000: Version 1.0.0
* 2013: Verison 3.0.2

>R packages

1.  The “base” R system contains, among other things, the base package which is required to run R and contains the most fundamental functions.
2.  The other packages contained in the “base” system include utils, stats, datasets, graphics, grDevices, grid, methods, tools, parallel, compiler, splines, tcltk, stats4.
3.  There are also “Recommend” packages: boot, class, cluster, codetools, foreign, KernSmooth, lattice, mgcv, nlme, rpart, survival, MASS, spatial, nnet, Matrix.

>R Resources

1. Available from CRAN (<http://cran.r-project.org>)
  *  *An Introduction to R*
  *  Writing R Extensions
  *  R Data Import/Export
  *  R Installation and Administration (mostly for building R from sources)
  *  R Internals (not for the faint of heart)

2.  Some Useful Books on S/R Some Useful Books on S/R
  Standard text
  *  Chambers (2008). **Software for Data Analysis**, Springer. 
  *  Chambers (1998). Programming with Data, Springer.
  *  Venables & Ripley (2002). Modern Applied Statistics with S, Springer.
  *  Venables & Ripley (2000). S Programming, Springer.
  *  Pinheiro & Bates (2000). Mixed-Effects Models in S and S-PLUS, Springer.
  *  Murrell (2005). R Graphics, Chapman & Hall/CRC Press.
  Other Resources
  *  Springer has a series of books called Use R!.
  *  A longer list of books is at <http://www.r-project.org/doc/bib/R-books.html>

###Getting help 

###R console Input and Evaluation




