---
title: "Lesson 1 -Part 2: Datatype"
author: "ZYY"
output: html_document
---

##R Objects

> Five basic or “atomic” classes of objects:

*  character
*  numeric (real numbers)
*  integer
*  complex
*  logical (True/False)

The most basic object is a vector

*  A vector can only contain objects of the same class
*  The one exception is a **list**
*  Empty vectors can be created with the **vector()** function.

##Attributes

* names, dimnames
* dimensions (e.g. matrices, arrays)
* class
* length
* other user-defined attributes/metadata
Attributes of an object can be accessed using the **attributes()** function.

###Numbers 

* Generally treated as numeric objects (i.e. double precision real numbers)
* If you explicitly want an integer, you need to specify the L suffix, i.e. 1L as 1(integer)
* Inf:infinity
* NaN: undefined value or missing value

###Vectors

The **c()** function can be used to create vectors of objects.
```{R}
x <- c(0.5, 0.6) ## numeric
x <- c(TRUE, FALSE) ## logical
x <- c(T, F) ## logical
x <- c("a", "b", "c") ## character
x <- 9:29 ## integer
x <- c(1+0i, 2+4i) ## complex
```

Using the **vector()** function
```{R}
x <- vector("numeric", length = 10) 
x
```
 
What if you create a vector and you mix two different types of objects?
e.g.
```{R} 
 y <- c(1.7, "a") ## character
 y <- c(TRUE, 2) ## numeric
 y <- c("a", TRUE) ## character
```
R will coerce the vector to create the least common denominator vector.

>Explicit Coercion

Objects can be explicitly coerced from one class to another using the ** as.XXX ** functions, if available
```{R}
x <- 0:6
class(x)
as.numeric(x)
as.logical(x)
as.character(x)
```
Nonsensical coercion results in *NA*s.
```{R}
x <- c("a", "b", "c")
as.numeric(x)
as.logical(x)
as.complex(x)
```

###List
Lists are a special type of vector that can contain elements of **different** classes.
```{R}
#To create a list
x <- list(1, "a", TRUE, 1 + 4i) 
x
```


###Matrices

Matrices are vectors with a **dimension** attribute.The dimension attribute is itself an integer vector of
length 2 (nrow, ncol).e.g.
```{R}
m <- matrix(nrow = 2, ncol = 3)
m
dim(m)
attributes(m)
```
Matrices are constructed **column-wise**, so entries can be thought of starting in the “upper left” corner
and running down the columns.
```{R}
m <- matrix(1:6, nrow = 2, ncol = 3) 
m
```
When create the matrices from a vector:
```{R}
 m <- 1:10
 m
 dim(m) <- c(2, 5)
 m
```
>Column/Row binding

```{R}
x <- 1:3
y <- 10:12
cbind(x, y)
rbind(x, y)
```

###Factor

* Used to represent categorical data.
* Ordered/Unordered
* Factors are treated specially by modelling functions like **lm()** and **glm()**
* Using factors with labels is better than using integers because **factors are self-describing**; having a variable that has values “Male” and “Female” is better than a variable that has values 1 and 2
```{R}
x <- factor(c("yes", "yes", "no", "yes", "no")) 
x
table(x)
unclass(x)  ##strips out the class for a vector
```

For ordered factors, the order of the levels can be set using the **levels** argument to **factor()**.
```{r}
x <- factor(c("yes", "yes", "no", "yes", "no"),
            levels = c("yes", "no"))
x

```

###Missing Values

NAN is used for undefined mathematical operations. And NA is pretty much used for everything else.
*  **is.na()** is used to test objects if they are NA
*  **is.nan()** is used to test for NaN
*  NA values have a class also, so there are **integer NA**, **character NA**, etc.
*  A NaN value is also NA but the converse is not true.

```{r}
x <- c(1, 2, NaN, NA, 4)
is.na(x)
is.nan(x)
```

###Data Frame

Used to store tabular data.
*  They are represented as a special type of list where every element of the list has to have the same length.
*  Data frames also have a special attribute called **row.names**
*  Data frames are usually created by calling **read.table()** or **read.csv()**
*  Can be converted to a matrix by calling **data.matrix()**

```{r}
x <- data.frame(foo = 1:4, bar = c(T, T, F, F))
x
nrow(x)
ncol(x)
```

###Names Attribute
R objects can also have names, which is very useful for writing **readable code** and **self-describing objects**.
```{r}
x <- 1:3
names(x)
names(x) <- c("foo", "bar", "norf")
x
names(x)
```

For lists:
```{r}
x <- list(a = 1, b = 2, c = 3)
x
```
For matrices, names are called **dimnames()**.
```{r}
m <- matrix(1:4, nrow = 2, ncol = 2)
dimnames(m) <- list(c("a", "b"), c("c", "d")) 
m
```

