---
title: "Overview of R"
author: "ZYY"
date: "2021年6月2日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background
When you want to get the **working directory**:
```{r }
getwd()
```
The reading and writing file should/will be in your working directory. If not, you will get a error message saying no such file or directory.

You can change your working directory in R in **File menu - Change dir**, then you can use dir command to list the files in working directory
```{r}
dir()
```

Besides files, you should also make sure that your r code or function in the working directory so that you can use it in the console window.
You can copy these codes into console window and run them or you can save them as an **.R** file, and use **source("filename.R")** command to run.

##Getting Started and R Nuts and Bolts

>Learning Objectives

By the end of week 1 you should be able to:

*  Install the R and RStudio software packages
*  Download and install the swirl package for R
*  Describe the history of the S and R programming lectures
*  Describe the differences between atomic data types
*  Execute basic arithmetic operations
*  Subset R objects using the "[", "[[", and "$" operators and logical vectors
*  Describe the explicit coercion feature of R
*  Remove missing (NA) values from a vector

###Overview and History if R
what is **R**?
It's basically R is a dialect of **S**.

Then what is **S**?

* Developed by John Chambers in 1976
* An internal statistical analysis environment.
* A FORTRAN library for statistical routines.
* Rewrited in the C language, i.e. Version 3,in 1988 with all the **statistical analysis functionality**.John Chambers and Trevor Hastie also published a semial book in the same year, called *the Statistical Models in S*, referred to **the white book** as well.
* *The book Programming with Data*(the green book) and Version 4 of S is released by John Chambers in 1998.
R is an implementation of the S language, in 1993 Bell Labs.

###Getting help 
###R console Input and Evaluation
###Data Types
####1. R 
