---
title: "Lesson 2 - Part 1: Control Structure"
author: "ZYY"
date: "2021年6月8日"
output: html_document
---

#Control Structures

* Control structures like if, while, and for allow you to control the flow of an R program
* Infinite loops should generally be avoided, even if they are theoretically correct.
* Control structures mentiond here are primarily useful for writing programs; for command-line interactive work, the **apply** functions are more useful.

##if, else: testing a condition

if(<condition>) {
 ## do something
} else {
 ## do something else
}

```{R}
x<-5
if(x > 3) {
 y <- 10
} else {
 y <- 0
}
y

#or you can do this
y <- if(x > 3) {
 10
} else {
 0
}
y
```

##for: execute a loop a fixed number of times

for(i in 1:10) {
 print(i)
}

```{r}
x <- c("a", "b", "c", "d")
#These 3 loops have the same behavior.
for(i in 1:4) {
 print(x[i])
}
for(i in seq_along(x)) {
 print(x[i])
}
for(letter in x) {
 print(letter)
}
for(i in 1:4) print(x[i])

```

for loops can be nested.Nesting beyond 2–3 levels is often very difficult to read/understand.
```{r}
x <- matrix(1:6, 2, 3)
for(i in seq_len(nrow(x))) {
 for(j in seq_len(ncol(x))) {
 print(x[i, j])
 }
}
```

##while: execute a loop while a condition is true

count <- 0
while(count < 10) {
 print(count)
 count <- count + 1
}
```{r}
z <- 5
while(z >= 3 && z <= 10) {
 print(z)
 coin <- rbinom(1, 1, 0.5)
 if(coin == 1) { ## random walk
 z <- z + 1
 } else {
 z <- z - 1
 }
}
```
Conditions are always evaluated from **left to right**.

##repeat: execute an infinite loop

The only way to exit a repeat loop is to call **break**.
e.g.
x0 <- 1
tol <- 1e-8
repeat {
 x1 <- computeEstimate()
 if(abs(x1 - x0) < tol) {
 break
 } else {
 x0 <- x1
 }
}

##break: break the execution of a loop
##next: skip an interation of a loop

for(i in 1:100) {
 if(i <= 20) {
 ## Skip the first 20 iterations
 next
 }
 ## Do something here
}

##return: exit a function

