---
title: 'Lesson 2 - Part 2: Function'
author: "ZYY"
date: "2021年6月8日"
output: html_document
---

#R Function

Functions in R are **“first class objects”**, which means that they can be treated much like any other R object.
* Functions can be passed as **arguments** to other functions
* Functions can be **nested**, so that you can define a function inside of another function
* The return value of a function is the **last expression** in the function body to be evaluated.

f <- function(<arguments>) {
 ## Do something interesting
}


Example 1:
```{r}
add2<-function(x,y){
  x+y
}
add2(3,5)
```

Example 2:
```{r}
above10<-function(x){
  use<- x>10
  x[use]
}
above10(a<-1:20)
```

Functions have **named arguments** which potentially have **default values**.
* The **formal arguments** are the arguments included in the function definition.
* The **formals** function returns a list of all the formal arguments of a function.
* Not every function call in R makes use of all the formal arguments.
* Function arguments can be **missing** or might have default values.

Example 3:
```{r}
above<-function(x,n=10){   #"n= 10"" is the default number.
  use <- x>n
  x[use]
}
above(1:20,4)
above(1:20)
formals(above)
```

Example 4:
```{r}
columnmean<- function (x,removeNA=TRUE){
  nc<- ncol(x)
  means<- numeric(nc)
  for (i in 1:nc){
    means[i]<-mean(x[,i],na.rm = removeNA)
  }
  means
}
columnmean(matrix(1:40,5,8))
```

R functions arguments can be matched **positionally** or by **name**.
You can mix positional matching with matching by name. When an argument is matched by name, it is “taken out” of the argument list and the remaining unnamed arguments are matched in the order that they are listed in the function definition.

Function arguments can also be **partially** matched: exact match for a named argument>partial match>positional match.

>Lazy Evaluation

Arguments to functions are evaluated lazily, so they are evaluated only as needed.

```{r}
f <- function(a, b) {
 a^2
}
f(2)
```
This function never actually uses the argument b, so calling f(2) will not produce an error because the 2 gets positionally matched to a.

##The “...” Argument
The ... argument indicate a variable number of arguments that are usually **passed on to other functions**.
* ... is often used when extending another function and you don’t want to copy the entire argument list of the original function.

e.g.
myplot <- function(x, y, type = "l", ...) {
 plot(x, y, type = type, ...)
}

*The ... argument is also necessary when the number of arguments passed to the function cannot be known in advance.
e.g. in paste(), the number of arguments can be flexible.

* Any arguments that appear after ... on the argument list must be **named explicitly** and cannot be partially matched.
```{r}
paste("a", "b", sep = ":")
paste("a", "b", se = ":")
```

#Scoping Rules
##Symbol binding
What if I named a function **lm** for square when R also has a function **lm** for linear modeling in the *stats* package?
When R tries to bind a value to a symbol, it searches through a series of **environments** to find the appropriate value. The search list can be found by:
```{r}
search()
```
When a user loads a package with **library** the namespace of that package gets put in position **2** of the search list (by default) and everything else gets shifted down the list.

R uses **lexical scoping** or static scoping, which turns out to be particularly useful for simplifying statistical computations.

##Lexical Scoping 

**The values of free variables are searched for in the environment in which the function was defined.**

In this case, z is called a **free variable**.
```{r}
f <- function(x, y) {
 x^2 + y / z
}
```

What is an environment?
* An environment is a collection of **(symbol, value)** pairs, i.e. x is a symbol and 3.14 might be its value.
* Every environment has a **parent environment**; it is possible for an environment to have multiple “children”
* The only environment without a parent is the empty environment.
* A function + an environment = a **closure** or function closure.

Searching for the value for a free variable:
* If the value of a symbol is not found in the environment in which a function was defined, then the search is continued in the **parent environment**.
* The search continues down the sequence of parent environments until we hit the **top-level environment**; this usually the **global environment (workspace)** or the **namespace of a package**.
* After the top-level environment, the search continues down the search list until we hit the **empty environment**. If a value for a given symbol cannot be found once the empty environment is arrived at, then an error is thrown.

```{r}
make.power <- function(n) {
 pow <- function(x) {
 x^n
 }
 pow
}
cube <- make.power(3)  #n<-3 
square <- make.power(2)  #n<-2
cube(3)
square(3)

```

What’s in a function’s environment?
```{r}
ls(environment(cube))
get("n", environment(cube))
ls(environment(square))
get("n", environment(square))
```

>Lexical vs. Dynamic Scoping Lexical vs. Dynamic Scoping

Example:
```{r}
y <- 10
f <- function(x) {
 y <- 2
 y^2 + g(x)
}
g <- function(x) {
 x*y
}
```
* With **lexical scoping** the value of y in the function g is looked up in the environment in which **the function was defined**, in this case the global environment, so the value of y is 10.
* With **dynamic scoping**, the value of y is looked up in the environment from which **the function was called** (sometimes referred to as the **calling environment**). So the value of y would be 2.
   -  In R the calling environment is known as the parent frame.

##Application: Optimization

