---
title: "Lesson 2 - Part 3"
author: "ZYY"
date: "2021年6月9日"
output: html_document
---

#Coding Standard

##1. Always use text files / text editor

##2. Indent your code

* Indenting improves readability
* Fixing line length (80 columns) prevents lots of nesting and very long functions
* Suggested: Indents of 4 spaces at minimum; 8 spaces ideal

##3. Limit the width of your code (80 columns?)
 
##4. Limit the length of individual functions


#Dates and Times

R has developed a special representation of dates and times
* Dates are represented by the **Date** class.
* Dates are stored internally as the number of days since **1970-01-01**.
* Dates can be coerced from a character string using the as.Date() function.
```{r}
x <- as.Date("1970-01-01")
x
unclass(x)
unclass(as.Date("1970-01-02"))
```

* Times are represented by the **POSIXct** or the **POSIXlt** class.
    - POSIXct is just a very large **integer** under the hood; it use a useful class when you want to store times in something like a **data frame**.
    - POSIXlt is a **list** underneath and it stores a bunch of other useful information like the day of the week, day of the year, month, day of the month.
* Times are stored internally as the number of seconds since **1970-01-01**
```{r}
x <- Sys.time()
x ## Already in ‘POSIXct’ format
unclass(x) #The number of secs
p <- as.POSIXlt(x)
names(unclass(p))
p$sec
```

* There are a number of generic functions that work on dates and times
    - **weekdays()**: give the day of the week
    - **months()**: give the month name
    - **quarters()**: give the quarter number (“Q1”, “Q2”, “Q3”, or “Q4”)
    
* **strptime()**:converts dates which are written in character string format into date or time objects.
```{r}
datestring <- c("January 10, 2012 10:40", "December 9, 2011 9:10")
x <- strptime (datestring, "%B %d, %Y %H:%M") #There is something wrong.
x
class(x)
```

##Operations on Dates and Times Operations on Dates and Times
```{r}
x <- as.Date("2012-01-01")
y <- strptime("9 Jan 2011 11:34:21", "%d %b %Y %H:%M:%S") #There is something wrong.
x <- as.POSIXlt(x)
x-y
```

