---
title: "Lesson 3 - Part 1: Loop Function"
author: "ZYY"
date: "2021年6月10日"
output: html_document
---

#lapply: Loop over a list and evaluate a function on each element

**lapply** takes three arguments: 
1. a list **X**; If X is not a list, it will be coerced to a list using **as.list.**
2. a function (or the name of a function) **FUN**; 
3. other arguments via its ... argument. 
```{r}
lapply
```
**lapply** always returns a list, regardless of the class of the input.
```{r}
x <- list(a = 1:5, b = rnorm(10))
lapply(x, mean)

x <- 1:4
lapply(x, runif) #generate a set of uniform random variables.The first argument in runif is the amount of variables.
lapply(x, runif, min = 0, max = 10) #min & max is arguments for runif. They are passed to lapply by "..." .
```

>Anonymous function

Anonymous functions are functions that don't have names, so you don't assign them a name of some sort but you can kind of generate them on the fly. For example:
```{r}
x <- list(a = matrix(1:4, 2, 2), b = matrix(1:6, 3, 2))
x
lapply(x, function(elt) elt[,1])
```
***
#sapply: Same as lapply but try to simplify the result
sapply will try to simplify the result of lapply if possible.
* If the result is a list where every element is length 1, then a **vector** is returned
* If the result is a list where every element is a vector of the same length (> 1), a **matrix** is returned.
* If it can’t figure things out, a **list** is returned.
```{r}
x <- list(a = 1:4, b = rnorm(10), c = rnorm(20, 1), d = rnorm(100, 5))
lapply(x, mean)
sapply(x, mean) 
```
***
#apply: Apply a function over the margins of an array

apply is used to a evaluate a function (often an anonymous one) over the margins of an array.
* It is most often used to apply a function to the rows or columns of a matrix
* It can be used with general arrays, e.g. taking the average of an array of matrices
* It is not really faster than writing a loop, but it works in one line!
```{r}
str(apply)
```
* **X** is an array
* **MARGIN** is an integer vector indicating which margins should be “retained”.
* **FUN** is a function to be applied
* **...** is for other arguments to be passed to FUN

```{r}
x <- matrix(rnorm(200), 20, 10)
apply(x, 2, mean) #MARGIN：dimension to be preserved. Row:1st dimension ; Col: 2nd dimension
apply(x, 1, sum)
apply(x, 1, quantile, probs = c(0.25, 0.75))# The 25% and 75% value of each row; 
                                            #probs argument is passed to quantile()
a <- array(rnorm(2 * 2 * 10), c(2, 2, 10))  #a 2*2*10 matrix
apply(a, c(1, 2), mean)                     #The average 2*2 matrix from 10 2*2 matrix
rowMeans(a, dims = 2)
```
> shortcut functions

* rowSums = apply(x, 1, sum)
* rowMeans = apply(x, 1, mean)
* colSums = apply(x, 2, sum)
* colMeans = apply(x, 2, mean)

***

#mapply: Multivariate version of lapply
mapply is a **multivariate apply** of sorts which applies a function in parallel over a set of arguments.
```{r}
 str(mapply)
```
* **FUN** is a function to apply.The number of arguments of **FUN** must greater(>=) than the argument in "...".
* **...** contains arguments to apply over
* **MoreArgs** is a list of other arguments to FUN.
* **SIMPLIFY** indicates whether the result should be simplified.
```{r}
mapply(rep, 1:4, 4:1)#list(rep(1, 4), rep(2, 3), rep(3, 2), rep(4, 1))
```
>Vectorizing a Function

```{r}
noise <- function(n, mean, sd) {
  rnorm(n, mean, sd)
  }
noise(5, 1, 2)      #5 variales with the mean 1 and standard variation 2.
noise(1:5, 1:5, 2)  #Acutally an error.
mapply(noise, 1:5, 1:5, 2)#list(noise(1, 1, 2), noise(2, 2, 2), noise(3, 3, 2), noise(4, 4, 2), noise(5, 5, 2))
```

***
#tapply: Apply a function over subsets of a vector
tapply is used to apply a function over subsets of a vector. 
```{r}
str(tapply)
```
* **X** is a vector
* **INDEX** is a factor or a list of factors (or else they are coerced to factors)
* **FUN** is a function to be applied
* **...** contains other arguments to be passed FUN
* **simplify**, should we simplify the result?
```{r}
x <- c(rnorm(10), runif(10), rnorm(10, 1))
f <- gl(3, 10) #f : factor variable.
f
tapply(x, f, mean)
tapply(x, f, mean, simplify = FALSE)  #The output when simplify = FALSE is a list.

```
***

#split
split takes a vector or other objects and splits it into groups determined by a factor or list of factors.
```{r}
str(split)
```
* **x** is a vector (or list) or data frame
* **f** is a factor (or coerced to one) or a list of factors
* **drop** indicates whether empty factors levels should be dropped.
By combining with split(), **lapply** and **sapply** can split the matrix into several part like *tapply* does.
```{r}
x <- c(rnorm(10), runif(10), rnorm(10, 1))
f <- gl(3, 10)
split(x, f)
lapply(split(x, f), mean)
```

>Splitting a Data Frame

```{r}
library(datasets)
head(airquality)
s <- split(airquality, airquality$Month)
lapply(s, function(x) colMeans(x[, c("Ozone", "Solar.R", "Wind")]))
sapply(s, function(x) colMeans(x[, c("Ozone", "Solar.R", "Wind")]))
sapply(s, function(x) colMeans(x[, c("Ozone", "Solar.R", "Wind")],
                               na.rm = TRUE))

```

>Splitting on More than One Level

```{r}
x <- rnorm(10)
f1 <- gl(2, 5)
f1
f2 <- gl(5, 2)
f2
interaction(f1, f2)   #Combine the 2 factors
str(split(x, list(f1, f2)))   # In split(), list(f1,f2) means interaction(f1, f2)
 str(split(x, list(f1, f2), drop = TRUE))   #Empty levels can be dropped.
```