---
title: 'Lesson 4 - Part 1 : Simulation '
author: "ZYY"
date: "2021年6月19日"
output: html_document
---

# str(): Structure
* A diagnostic fuction and an alternative to **sumary()**.
* Particularly suited to **compactly display** large lists which may contain nested lists.
```{r}
str(str)
str(lm)
x<-rnorm(100,2,4)
summary(x)
str(x)
#factor
f<-gl(40,10)
summary(f)
str(f)
#dataframe
library(datasets)
head(airquality)
str(airquality)
#matrix
m<-matrix(rnorm(100),10,10)
str(m)
m[,1]
s<-split(airquality,airquality$Month)
str(s)
```

#Simulation

* **rnorm**: generate random **Normal** variates with a given **mean** and **standard deviation**.
* **dnorm**: evaluate the **Normal probability density** (with a given mean/SD) at a point (or vector of points)
* **pnorm**: evaluate the **cumulative distribution** function for a Normal distribution

* **rpois**: generate random **Poisson** variates with a given rate.

>Probability distribution functions usually have four functions associated with them:

Standard distributions are built in: Normal, Poisson, Binomial, Exponential, Gamma, etc.
* **d** for density
* **r** for random number generation
* **p** for cumulative distribution
* **q** for quantile function
```{r}
#dnorm(x, mean = 0, sd = 1, log = FALSE)
#pnorm(q, mean = 0, sd = 1, lower.tail = TRUE, log.p = FALSE)
#qnorm(p, mean = 0, sd = 1, lower.tail = TRUE, log.p = FALSE)
#rnorm(n, mean = 0, sd = 1)
x <- rnorm(10)
x
x <- rnorm(10, 20, 2) 
x
summary(x)
```

## **set.seed()**: ensures reproducibility.
Always set the random number seed when conducting a simulation!
```{r}
set.seed(1)
rnorm(5)
rnorm(5)
set.seed(1)
rnorm(5)#After reset the seed, the random number can be reproduced.
```

##Poisson data
```{r}
rpois(10, 1)
rpois(10, 2)
rpois(10, 20)
ppois(2, 2)
ppois(4, 2)
ppois(6, 2)
```

##Generating random numbers from a linear model

Suppose we want to simulate from the following linear model:

y = β0 + β1x + ε

where ε~$N (0.2^2). Assume x~$N （0，1^2), and β0 = 0.5, β1 = 2.
```{r}
set.seed(20)
x <- rnorm(100)
e <- rnorm(100, 0, 2)
y <- 0.5 + 2 * x + e
summary(y)
plot(x, y)
```

What if x is binary?
```{r}
set.seed(10)
x <- rbinom(100, 1, 0.5)
e <- rnorm(100, 0, 2)
y <- 0.5 + 2 * x + e
summary(y)
plot(x, y)
```

Suppose we want to simulate from a **Poisson** model where

Y ~ Poisson(μ)

log μ = β0 + β1x
and β0 = 0.5 and β1=0.3 . We need to use the **rpois** function for this
```{r}
set.seed(1)
x <- rnorm(100)
log.mu <- 0.5 + 0.3 * x
y <- rpois(100, exp(log.mu))
summary(y)
plot(x, y)
```

##Random sampling
The **sample** function draws randomly from a specified set of (scalar) objects allowing you to sample from arbitrary distributions.
```{r}
set.seed(1)
sample(1:10, 4)
sample(1:10, 4)
sample(letters, 5)
sample(1:10) ## permutation
sample(1:10, replace = TRUE) ## Sample w/replacement
```